Make any stupid plot you want

### 2020-12-10 draft/sections/math.tex
latex is borked

\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_1k.png}
    %% add box around neighboring P and Map
    \label{fig:k_data}
\end{figure}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_2k.png}
\end{figure}

@@

% preamble type intro to displays, examples - displays can include screen, 3D printer, sphereical display, H is the total space of the screen. 11

The sets correspond to the sections on $\S$, which is the topology of the output of the artist $A$. The space $H$ is a total space representing the predisplay space, with a fiber dependent on the render space and a base space of $\S$:
\begin{equation}
    \begin{tikzcd}
        D \arrow[r, hook] & H \arrow[d, "\pi" description, bend right] \\
                                    & S \arrow[u, "\rho" description, bend right] 
    \end{tikzcd}
\end{equation}

@@

\subsection{Artist}
What is A supposed to preserve?

@@

As described in section~\ref{sec:display}, $rho: S \rightarrow H$ is composed of subfunctions that are dependent on the prerender fiber $D$. In the case of a screen
\begin{equation}
    \rho (\alpha, \beta) = (\rho_X(\alpha, \beta), \rho_Y(\alpha, \beta), \rho_Z(\alpha, \beta), \rho_B(\alpha, \beta), \rho_G(\alpha, \beta), \rho_B(\alpha, \beta), \rho_A(\alpha, \beta))
\end{equation}

where $(\alpha, \beta)$ are coordinates on $S$. The mapping $Q: \Gamma(\tau) \rightarrow D$ builds $\rho$ functions on $S$ by compositing $\nu: c \mapsto v \subset {x,y,z,r,g,b,a}$ functions that map data in some field $c$ to a subset of display variables.

\begin{equation}
    \begin{tikzcd}
        \Gamma(\tau) \arrow[rr, "{Q(\nu_{0}(c),\ldots,\nu_n(c))}"] &  & {\rho_X, \rho_Y, \rho_Z, \rho_R, \rho_B, \rho_G, \rho_A}
    \end{tikzcd}
    \label{eq:Q}
\end{equation}

$Q$ composites $\nu$ functions because multiple mappings can target the same field in $D$, for example y position and linewidth will concurrently affect where a pixel is drawn on screen.

>>>>

\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_1k.png}
    %% add box around neighboring P and Map
    \label{fig:k_data}
\end{figure}

\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_2k.png}
\end{figure}

@@

% preamble type intro to displays, examples - displays can include screen, 3D printer, sphereical display, H is the total space of the screen. 11
Every point $k \in K$ maps to a space $S_{k} \in S$, which is the topology of the output of the artist $A$. The space $H$ is a total space representing the predisplay space, with a fiber dependent on the render space and a base space of $\S$:
\begin{equation}
    \begin{tikzcd}
        D \arrow[r, hook] & H \arrow[d, "\pi" description, bend right] \\
                                    & S \arrow[u, "\rho" description, bend right] 
    \end{tikzcd}
\end{equation}

@@

\subsection{Artist)

@@

As described in section~\ref{sec:display}, $rho: S \rightarrow H$ is composed of subfunctions that are dependent on the prerender fiber $D$. In the case of a screen where $D=\mathbb{R}^{7}$

\begin{equation}
    \rho (u, v) = (\rho_X(u, v), \rho_Y (u, v), \rho_Z (u, v), \rho_B (u, v), \rho_G (u, v), \rho_B (u, v), \rho_A (u, v))
\end{equation}

where $(u,v)$ are coordinates of a point on $S$. The map reduce function $Q: F\rightarrow \rho$ builds $\rho$ functions on $S$ by compositing $\nu_{param}: c \mapsto \rho_{d \in D}$ functions that map data in some field $c$ to a subset of visual variables such as position or color\cite{bertinIIPropertiesGraphic2011, munznerChDataAbstraction} that are identified as parameters to the artist function.

\begin{equation}
     \rho(u, v) = Q(\nu_param_{0}(\tau_{c_0}), \ldots \nu_param_{n}(\tau_{c_n}))(u,v)
    \label{eq:Q}
\end{equation}

$Q$ composites $\nu$ functions because multiple parameters can target the same field in $D$, for example $\nu_{ypos}$ and $\nu_{linewidth}$ together determine the y position of a line drawn on screen such that $Q: \nu_{ypos}, \nu_{linewidth} \rightarrow \rho_{Y}$
